Towards Spherical Robots for Mobile Mapping in Human Made Environments\tnoteref{mytitlenote}

### 2021-07-12 Latex/sections/registration.tex
Minor changes in math formatting

Assuming we now know the Hesse-normal form of all planes and all assigned points to these planes, we register the points to have a minimal distance to their respective planes.
The transformation $T(\vec{p}_i)$ of each point $\vec{p}_i$ with respect to a 6 DoF motion is described in homogeneous coordinates using the roll-pitch-yaw ($\varphi-\vartheta-\psi$) Tait-Brian angles as in~\cite{diebel2006representing}. Transforming the result back from homogeneous coordinates and using $C_a$ and $S_a$ to denote the cosine and sine of the angle in the subscript, and $t_a$ denoting the translation along the axis in the subscript yields:
\begin{align}
	T(\vec{p}_i)  =
    \resizebox{0.35\textwidth}{!}{$\begin{bmatrix}
        x_i C_\vartheta C_\psi - y_iC_\vartheta S_\psi + z_i S_\vartheta + t_x\\
        x_i (C_\varphi S_\psi + C_\psi S_\varphi S_\vartheta) + y_i(C_\varphi C_\psi - S_\varphi S_\vartheta S_\psi) - z_i C_\vartheta S_\varphi + t_y\\
        x_i(S_\varphi S_\psi - C_\varphi C_\psi S_\vartheta) + y_i(C_\psi S_\varphi + C_\varphi S_\vartheta S_\psi) + z_i C_\varphi C_\vartheta + t_z
    \end{bmatrix}$}
\end{align}
From this we define the function $D(\varphi,\vartheta,\psi,t_x,t_y,t_z, \vec{p}_i)$ that computes the distance of a point $\vec{p}_i$ to its corresponding plane $\mathcal{P}_k$.
Omitting the arguments of the function for simplicity:
\begin{align}
\begin{aligned}
    D &= T(\vec{p}_i) \cdot \vec{n}_{\mathcal{P}_k} \\
      &= n_{\mathcal{P}_k}^x (x_i C_\vartheta C_\psi - y_iC_\vartheta S_\psi + z_i S_\vartheta + t_x)\\
       &+ n_{\mathcal{P}_k}^y(x_i (C_\varphi S_\psi + C_\psi S_\varphi S_\vartheta)\\
       &\qquad+ y_i(C_\varphi C_\psi - S_\varphi S_\vartheta S_\psi) - z_i C_\vartheta S_\varphi + t_y)\\
       &+ n_{\mathcal{P}_k}^z (x_i(S_\varphi S_\psi - C_\varphi C_\psi S_\vartheta)\\
       &\qquad+ y_i(C_\psi S_\varphi + C_\varphi S_\vartheta S_\psi) + z_i C_\varphi C_\vartheta + t_z)\\
       &- \rho_{\mathcal{P}_k}
\end{aligned}
\end{align}

>>>>

Assuming we now know the Hesse-normal form of all planes and all assigned points to these planes, we register the points to have a minimal distance to their respective planes.
The transformation $T(\vec{p}_i)$ of each point $\vec{p}_i$ with respect to a 6 DoF motion is described in homogeneous coordinates using the roll-pitch-yaw ($\varphi-\vartheta-\psi$) Tait-Brian angles as in~\cite{diebel2006representing}. Transforming the result back from homogeneous coordinates and using $C_a$ and $S_a$ to denote the cosine and sine of the angle in the subscript, and $t_a$ denoting the translation along the axis in the subscript yields:
\begin{align}
	T(\vec{p}_i)  =
    \resizebox{0.35\textwidth}{!}{$\begin{bmatrix}
        x_i C_\vartheta C_\psi - y_iC_\vartheta S_\psi + z_i S_\vartheta + t_x\\
        x_i (C_\varphi S_\psi + C_\psi S_\varphi S_\vartheta) + y_i(C_\varphi C_\psi - S_\varphi S_\vartheta S_\psi) - z_i C_\vartheta S_\varphi + t_y\\
        x_i(S_\varphi S_\psi - C_\varphi C_\psi S_\vartheta) + y_i(C_\psi S_\varphi + C_\varphi S_\vartheta S_\psi) + z_i C_\varphi C_\vartheta + t_z
    \end{bmatrix}$}
\end{align}
From this we define the function $D(\varphi,\vartheta,\psi,t_x,t_y,t_z, \vec{p}_{i})$ that computes the distance of a point $\vec{p}_{i}$ to its corresponding plane $\mathcal{P}_k$.
Omitting the arguments of the function for simplicity:
\begin{equation}
\begin{split}
    D &= T(\vec{p}_i) \cdot \vec{n}_{\mathcal{P}_k} \\
      &= n_{\mathcal{P}_k}^x (x_i C_\vartheta C_\psi - y_iC_\vartheta S_\psi + z_i S_\vartheta + t_x)\\
       &+ n_{\mathcal{P}_k}^y(x_i (C_\varphi S_\psi + C_\psi S_\varphi S_\vartheta)\\
       &\qquad+ y_i(C_\varphi C_\psi - S_\varphi S_\vartheta S_\psi) - z_i C_\vartheta S_\varphi + t_y)\\
       &+ n_{\mathcal{P}_k}^z (x_i(S_\varphi S_\psi - C_\varphi C_\psi S_\vartheta)\\
       &\qquad+ y_i(C_\psi S_\varphi + C_\varphi S_\vartheta S_\psi) + z_i C_\varphi C_\vartheta + t_z)\\
       &- \rho_{\mathcal{P}_k}
\end{split}
\end{equation}
